\documentclass[11pt]{article}

\usepackage[margin=1in]{geometry}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage[hidelinks,pageanchor=false]{hyperref}
\usepackage{enumitem}

\setlength{\parindent}{0pt}
\setlength{\parskip}{0.65em}
\pagenumbering{gobble}
\sloppy

\begin{document}

\begin{center}
{\Large\bfseries Title Page}\\[1.5em]
{\LARGE\bfseries Improving Recognition of Overlapping Human Speech on Single-Microphone Social Robots with Streaming Two-Mask CMGAN Post-Filtering}\\[1em]
{\large Submitted to ACM Transactions on Human-Robot Interaction (THRI)}
\end{center}

\vspace{1em}

\section*{Authors}

\textbf{Yue Li}\\
Vrije Universiteit Amsterdam\\
Amsterdam, Netherlands\\
\href{mailto:y6.li@vu.nl}{y6.li@vu.nl}\\
ORCID: \href{https://orcid.org/0000-0002-5624-7235}{0000-0002-5624-7235}

\textbf{Florian Kunneman}\\
Utrecht University\\
Utrecht, Netherlands\\
\href{mailto:f.a.kunneman@uu.nl}{f.a.kunneman@uu.nl}\\
ORCID: \href{https://orcid.org/0000-0002-1932-3200}{0000-0002-1932-3200}

\textbf{Koen Hindriks}\\
Vrije Universiteit Amsterdam\\
Amsterdam, Netherlands\\
\href{mailto:k.v.hindriks@vu.nl}{k.v.hindriks@vu.nl}\\
ORCID: \href{https://orcid.org/0000-0002-5707-5236}{0000-0002-5707-5236}

\section*{Corresponding Author}

Yue Li, \href{mailto:y6.li@vu.nl}{y6.li@vu.nl}.

\section*{Author Contributions}

Yue Li: Conceptualization, Methodology, Software, Validation, Formal Analysis,
Investigation, Data Curation, Visualization, Writing -- Original Draft, Project
Administration.

Florian Kunneman: Supervision, Writing -- Review \& Editing, Conceptualization
and Methodology feedback.

Koen Hindriks: Supervision, Writing -- Review \& Editing, Conceptualization and
Methodology feedback.

All authors reviewed and approved the final manuscript.

\section*{Acknowledgements}

The authors thank the study participants for their time.

\section*{Funding}

This work was supported by the Chinese Scholarship Council.

\section*{Conflicts of Interest}

The authors declare no conflicts of interest.

\section*{Ethics Statement}

The research ethics self-check of the Ethics Review Committee of the Faculty of
Science (BETHCIE), Vrije Universiteit Amsterdam, completed on 01/02/2025,
indicated that this project does not require further evaluation by the Research
Ethics Review Committee. All participants provided informed consent prior to
recording.

\section*{Data and Code Availability}

Code, scripts, and anonymized derived materials supporting this study will be
made available in a public GitHub repository. Raw participant audio recordings
are not publicly released because they may contain identifiable voice data;
access may be considered upon reasonable request subject to consent, ethics, and
privacy constraints.

\end{document}
